\NeedsTeXFormat{LaTeX2e}
[2018/12/01 v1.0 Two Column Curriculum Vitae]

\LoadClass[10pt]{scrartcl}

\setcounter{secnumdepth}{-1}
\RequirePackage[hmargin=1.25cm,vmargin=1.25cm,twocolumn,columnsep=1.25cm]{geometry}
\RequirePackage{bookman,etoolbox,hyperref,marvosym,needspace,tabularx,xcolor}

% Capitalize words of at least a minimum length (default to 3 chars).
% The text is capitalized before being expanded.
%
% This macro uses Lua to do the job but fails gracefully (that is,
% return the text as is) if \directlua is not available.
%
% |[
% \ucwords[optional: miminum length]{text}
% ]|
\newcommand\ucwords[2][3]{%
    % Fails gracefully if not in LuaLaTeX
    \providecommand\directlua[1]{#2}%
    \directlua{%
	local minlen=tonumber("#1")
	local src="\luaescapestring{\unexpanded{#2}}"
	local dst={}
	for w in src:gmatch('[^\string\%s]+') do
	    if w:len() >= minlen then w = w:sub(1,1):upper()..w:sub(2) end
	    table.insert(dst, w)
	end
	tex.print(dst)}}

\pagestyle{empty}
\setlength\parindent{0pt}
\color[HTML]{303030} % Default foreground color
\definecolor{link}{HTML}{506060} % Hyperlinks
\hypersetup{colorlinks,breaklinks,urlcolor=link,linkcolor=link}
\setkomafont{disposition}{\color[HTML]{801010}}
\setkomafont{section}{\scshape\Large\mdseries}

% In tccv \part must contain the subject of the curriculum vitae.
% The command will start a new page and output in onecolumn the
% subject (first and last name) with the hardcoded text
% "Curriculum vitae" under it.
%\renewcommand\part[1]{%
%    \twocolumn[%
%    \begin{center}
%	\vskip-\lastskip%
%	{\usekomafont{part} #1} \medskip\\
%	{\fontfamily{pzc}\selectfont\Huge Curriculum vitae}
%	\bigskip
%   \end{center}]}

% Overrides the \section command to capitalize every
% word for cosmetic purposes and draws a rule under it.
\makeatletter
\let\old@section\section
\renewcommand\section[2][]{%
    \old@section[#1]{\ucwords{#2}}%
    \newdimen\raising%
    \raising=\dimexpr-0.7\baselineskip\relax%
    \vskip\raising\hrule height 0.4pt\vskip-\raising}
\makeatother

% Allow conditionals based on the job name. This can usually be set
% from a command-line argument: check fausto.en.tex for an example.
%
% |[
% \ifjob{jobname}{content if matches}{content if does not match}
% ]|
\newcommand\ifjob[3]{%
    \edef\JOBNAME{\jobname}%
    \edef\PIVOT{\detokenize{#1}}%
    \ifdefstrequal{\JOBNAME}{\PIVOT}{#2}{#3}%
}

% Renders a personal data box:
%
% |[
% \personal[optional: web site without scheme (no http:// prefix)]
%          {address}{phone number}{email}
% ]|
\newcommand\personal[4][]{%
    \needspace{0.5\textheight}%
    \newdimen\boxwidth%
    \boxwidth=\dimexpr\linewidth-2\fboxsep\relax%
    \colorbox[HTML]{F5DD9D}{%
    \begin{tabularx}{\boxwidth}{c|X}
    \Writinghand & {#2}\smallskip\\
    \Telefon     & {#3}\smallskip\\
    \Letter      & \href{mailto:#4}{#4}
    \ifstrempty{#1}{}{\smallskip\\ \Lightning & \href{http://#1}{#1}}
    \end{tabularx}}}

% Every \item can be followed by one or more paragraphs
% of description:
%
% |[
% \item{date range}{company}{role}
%
% Description of what achieved during this application.
% ]|
\newenvironment{eventlist}{%
    \newcommand*\inskip{}
    \renewcommand\item[3]{%
	\inskip%
	{\raggedleft\textsc{##1}\\[1pt]}
	{##2}\\[2pt]
	{\Large\textit{##3}}
	\medskip
	\renewcommand\inskip{\bigskip}}}
    {\bigskip}

% Use only \item inside this environment: no other macros
% are allowed:
%
% |[
% \item[optional: what has been achieved]{years}{subject}{notes}
% ]|
\newenvironment{yearlist}{%
    \renewcommand\item[4][]{%
	{\textsc{##2}} & {\bfseries ##3} \\
	\ifstrempty{##1}{}{& {\textsc{##1}} \\}
	& {\textit{##4}}\medskip\\}
    \tabularx{\linewidth}{rX}}
    {\endtabularx}


% Use only \item inside this environment: no other macros
% are allowed:
%
% |[
% \item{fact}{description}
% ]|
\newenvironment{factlist}{%
    \newdimen\unbaseline
    \unbaseline=\dimexpr-\baselinestretch\baselineskip\relax
    \renewcommand\item[2]{%
	\textsc{##1} & {\raggedright ##2\medskip\\}\\[\unbaseline]}
    \tabularx{\linewidth}{rX}}
    {\endtabularx}
%%
%% End of `tccv' section
%%\usepackage[english]{babel}
\begin{document}

\part{Gautam Jha}

\section{Work experience}

\begin{eventlist}

\item{April 2018 -- Present}
     {SDE3, Adobe Systems, Bangalore}
     {Dreamweaver and Brackets}
     
Currently work on \href{https://www.adobe.com/in/products/dreamweaver.html}{Dreamweaver} maintenance and enhancements. Also contribute to Adobe's open-source, CEF based Text Editor, \href{https://github.com/adobe/brackets}{Brackets}

I am using C, Objective-C, C++98/11/14/17, JS, Cocoa, MFC, CEF to deliver my work.

\item{August 2016 -- April 2018}
     {SDE2, Adobe Systems, Noida, India}
     {PDF/PS Print and Scan on SOCs}

Worked on maintenance, enhancement and porting of Adobe Postscript and PDF RIP(Raster Image Processor). Apart from bug fixes and enhancements, porting the product to different SOC and RTOS combinations was important part of my role.

I used C, C++98/11, PDF, PostScript and Linux (Desktop, RTOSs) to deliver my work.

\item{January 2015 -- August 2016}
     {Sr SE, PIMCO(Contractor)}
     {C++ financial number crunching}

Enhanced and maintained financial analytics software-suite responsible for calculating risk numbers for Fixed Income Instruments. Reducing the run-time of different modules was primary part of my role. Also Maintained infra-structure libraries like Memcached, caching etc.
Ideated and implemented a small declarative language to control command line argument
parsing and validations (CLAP).

Used C++11, Oracle, Sybase C API, Memcached C API, Valgrind, Flex, Bison, GCC, GDB, GNU
MAKE, CMAKE, Boost CPP Libs, Linux to deliver my tasks.

\item{January 2013 -- January 2015}
     {Consultant, FICO, Bangalore, India}
     {FICO-CCS, Rule Engines}

Worked with BAs in analyzing the client requirements for the product FICO-CCS.
Customized, implemented, maintained and supported the product for different banks.
Maintained and enhanced legacy C and C++ code base for the product.
Wrote Tools to automate daily work as well as for information retrieval from the System.

Used C, C++98, Python2.7, MySQL, Linux, XML, XSLT, XSD, YAML, FreeMarker and FICO
proprietary rule engines to deliver my tasks.
\end{eventlist}

\personal
    {Bangalore, India}
    {+91 9731 734217}
    {gautam0217@gmail.com}
    
\section{Profile Summary}
\begin{itemize}
    \item{7 years of experience in Software Development with proficiency in Data Structures, Algorithms, Design Patterns, C++, C, JavaScript, Python and Shell Scripting.}
    \item{C++ Enthusiast with knowledge of memory models, threading models, microprocessor instructions and compiler concepts.}
    \item{Worked on C++ Templates, Policy based designs and meta-programming.}
    \item{Come up with internal-tooling, automation, build system improvement ideas and implementations.}
    \item{Good knowledge of OS internals and feature, especially Linux.}
    \item{Work on Agile Software Development Methodology.}
    \item{Worked with PIMCO and FICO, and have domain experience in debt-markets, financial
analytics, and rule-engines.}
    \item{Have strong Mathematics foundations}
\end{itemize}

\section{Education}

\begin{yearlist}

\item {2010 -- 2013}
     {Masters Computer Applications (MCA)}
     {JNU, New Delhi, India}

\item[Mathematics and Physics]{2006 -- 2009}
    {Bachelor of Science(B.Sc.)}
    {Gov. Post Graduation College, Obra, Sonbhadara, UP, India}

\end{yearlist}

\section{Communication skills}

\begin{factlist}
\item{Hindi}{Oral: good -- Written: good}
\item{English}{Oral: fair -- Written: good}
\end{factlist}

\section{Social}
\begin{itemize}
\item \href{https://stackoverflow.com/users/4373992/jha-g}{Stack Overflow}
\item \href{https://github.com/jha-g}{Github}
\item \href{https://www.linkedin.com/in/gautam0217}{Linkedin}
\end{itemize}

\end{document}
